{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
Small correction

			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared spectrum which we will use for the simulation and application. This continuous underlying process for which 
 $x_i(t)$ exists $\forall t \in [T_1, T_2]$ is only observed at the discrete measurement points. This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

@@

    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. 
    Both functions were created such that the inner product $\langle NIR_{sim}, f \rangle, f \in \{f_1(t), f_2(t)\}$ creates responses similar to the original octane ratings of the gasoline dataset.

@@

	\subsection{Results}
	{\color{green}DESCRIBE RESULTS: make paragraph for each setup? so 6 paragraphs? Like this: }

@@

>>>>

			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}. This continuous underlying process for which 
 $x_i(t)$ exists $\forall t \in [T_1, T_2]$ is only observed at the discrete measurement points. This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:

@@

    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline dataset.

@@

	\subsection{Results}

@@

	\subsection{Near-infrared (NIR) Spectroscopy}
	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm). It therefore measures the absorption and interaction of this spectrum of radiation with the sample. NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another big advantage is that it does not need a reagent and thus does not destroy the sample. It is used for analysis in different sectors and fields, like the agrochemical industry but also in healthcare. Its non-invasive nature makes it also to an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy is able to detect the worsening of the blood glucose metabolic dysfunction (cf . \cite{FR_li_et_al_2020}). In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy. According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (eg.: carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules). While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al. 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characktersitics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
